Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-10 manuscript.qmd
change risk figure to vertical layout

![Histograms over the predicted risk of occult involvement in contralateral LNL II (left), III (middle), and IV (right), shown for various combinations of T-category, tumor lateralization, and clinical LNL diagnoses. All LNLs not explicitly mentioned in the legend, including the LNL for which the risk of occult disease was computed, were assumed to be clinically negative (specificity 76%, sensitivity 81%).](figures/fig_model_risks.svg){#fig-model-risks}

>>>>

![Histograms over the predicted risk of occult involvement in contralateral LNL II (top), III (middle), and IV (bottom), shown for various combinations of T-category, tumor lateralization, and clinical LNL diagnoses. All LNLs not explicitly mentioned in the legend, including the LNL for which the risk of occult disease was computed, were assumed to be clinically negative (specificity 76%, sensitivity 81%).](figures/fig_model_risks.svg){#fig-model-risks width="50%"}
